### 2015-10-10 README.Rmd
updated readme

```{r}
library(qmj)
data(companies) #Stores company names and tickers from the Russell 3000 index
data(financials) #Stores financial documents for the given list of companies.
data(prices) # Stores price returns and closing stock prices for the past two years.
data(quality) #Stores the quality scores and the scores of its components.
```

>>>>

```{r}
library(qmj)
data(companies) ## Stores company names and tickers from the Russell 3000 index.
data(financials) ## Stores financial documents for the given list of companies.
data(prices) ## Stores price returns and closing stock prices for the past two years.
data(quality) ## Stores the quality scores and the scores of its components.
```
